---
title: "Stepwise for Quantile Regression"
author: "RD"
date: "March 18, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We wanted to test a step-wise quantile regression to understand the features that impact more the model, we need to compute every quartile:

```{r}
stepfit0_10 <- step(rq(price ~ ., data = airbnb, tau = 0.1), direction = "both")
```

```{r}
summary(stepfit0_10)
```

```{r}
rho <- function(u,tau=.5)u*(tau - (u < 0))
fit0_10 <- rq(price ~ 1,tau=0.1, data=airbnb)
pseudo_r2_0_10 <- 1- stepfit0_10$rho/fit0_10$rho
pseudo_r2_0_10
```

For quartile 0.25:

```{r}
stepfit0_25 <- step(rq(price ~ ., data = airbnb, tau = 0.25), direction = "both")
```

```{r}
summary(stepfit0_25)
```

```{r}
rho <- function(u,tau=.5)u*(tau - (u < 0))
fit0_25 <- rq(price ~ 1,tau=0.25, data=airbnb)
pseudo_r2_0_25 <- 1- stepfit0_25$rho/fit0_25$rho
pseudo_r2_0_25
```

For quartile 0.50:

```{r}
stepfit0_50 <- step(rq(price ~ ., data = airbnb, tau = 0.5), direction = "both")
```

```{r}
summary(stepfit0_50)
```

```{r}
rho <- function(u,tau=.5)u*(tau - (u < 0))
fit0_50 <- rq(price ~ 1,tau=0.5, data=airbnb)
pseudo_r2_0_50 <- 1- stepfit0_50$rho/fit0_50$rho
pseudo_r2_0_50
```

For quartile 0.25:

```{r}
stepfit0_75 <- step(rq(price ~ ., data = airbnb, tau = 0.75), direction = "both")
```

```{r}
summary(stepfit0_75)
```

```{r}
rho <- function(u,tau=.5)u*(tau - (u < 0))
fit0_75 <- rq(price ~ 1,tau=0.75, data=airbnb)
pseudo_r2_0_75 <- 1- stepfit0_75$rho/fit0_75$rho
pseudo_r2_0_75
```

For quartile 0.90:

```{r}
stepfit0_90 <- step(rq(price ~ ., data = airbnb, tau = 0.9), direction = "both")
```

```{r}
summary(stepfit0_90)
```

```{r}
rho <- function(u,tau=.5)u*(tau - (u < 0))
fit0_90 <- rq(price ~ 1,tau=0.9, data=airbnb)
pseudo_r2_0_90 <- 1- stepfit0_90$rho/fit0_90$rho
pseudo_r2_0_90
```

With step-wise procedure:

Quantile 0.10 <- pseudo R^2 = 0.31
Quantile 0.25 <- pseudo R^2 = 0.37
Quantile 0.50 <- pseudo R^2 = 0.37
Quantile 0.75 <- pseudo R^2 = 0.32
Quantile 0.90 <- pseudo R^2 = 0.22

The quantile regression model with step-wise selection:

- Quantile 0.10: -846.24
- Quantile 0.25: -5511.20
- Quantile 0.50: -6571.02
- Quantile 0.75: -2302.18
- Quantile 0.90: 5044.44
